\documentclass[11pt,a4paper]{article}


\usepackage[margin=0.65in]{geometry} 
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}


\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=teal,
}


\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}


\newcommand{\cventry}[4]{
    \noindent \textbf{#1} \hfill \textit{#2} \\
    \noindent \textit{#3} \hfill #4 \vspace{3pt}
}

\begin{document}


\pagestyle{empty}


\begin{center}
    {\Huge \textbf{Nil Blanco}}\\[6pt]
    Barcelona, Spain $\cdot$ EU Citizen $\cdot$ +34 600 000 000 \\
    \href{mailto:email@gmail.com}{email@gmail.com} $\cdot$ \href{https://github.com/Nil-Blanco}{https://github.com/Nil-Blanco}
\end{center}

\vspace{6pt}


\section{Education}

\cventry{Technical University of Munich (TUM)}{Munich, Germany}{Erasmus Exchange Program (BSc Physics)}{Oct 2024 -- Sep 2025}
\begin{itemize}[leftmargin=*, nosep]
    \item Selected for a competitive 11-month academic exchange at one of Europe's top-tier technical universities.
    \item Adapted to a high-performance international environment, completing advanced coursework in physical sciences.
\end{itemize}
\vspace{6pt}

\cventry{Universitat de Barcelona (UB)}{Barcelona, Spain}{Bachelor of Science in Physics}{Sep 2021 -- Jan 2026}
\begin{itemize}[leftmargin=*, nosep]
    \item Developed strong analytical and problem-solving skills through rigorous mathematical modeling and theoretical physics.
\end{itemize}


\section{Technical \& Research Projects}

\cventry{Numerical Simulation of Gravitational Waves (LISA Mission)}{Academic Research}{Data Analysis \& Mathematical Modeling}{Nov 2025 -- Present}
\begin{itemize}[leftmargin=*, nosep]
    \item Developed numerical models to simulate complex physical signals and timing residuals related to the Laser Interferometer Space Antenna (LISA).
    \item Applied Schwarzschild-de Sitter metrics to solve advanced non-linear equations, demonstrating capacity for high-level abstract mathematical reasoning.
    \item \textbf{Manuscript in preparation:} Currently co-authoring a comprehensive research paper based on these findings for publication in a peer-reviewed scientific journal, in collaboration with researchers from ICCUB.
\end{itemize}
\vspace{6pt}

\cventry{Algorithmic Trading Bot Development}{Personal Project}{Quantitative Trading \& Backtesting}{May 2026 -- Present}
\begin{itemize}[leftmargin=*, nosep]
    \item Programmed a custom algorithmic trading bot in Python to simulate and evaluate automated market strategies.
    \item Developed and backtested Long/Short and Parabolic SAR trading models utilizing extensive historical market data.
    \item Applied data analysis and statistical validation to optimize technical indicators and risk management parameters.
\end{itemize}

\section{Professional Experience}

\cventry{Generalitat de Catalunya}{Catalonia, Spain}{Mathematics Educator}{Mar 2026 -- Present}
\begin{itemize}[leftmargin=*, nosep]
    \item Translate complex mathematical concepts into clear, accessible frameworks for diverse audiences.
    \item Design, structure, and format quantitative assessments and technical documentation using LaTeX.
    \item Manage classroom dynamics and optimize learning processes, demonstrating strong communication and leadership skills.
\end{itemize}


\section{Skills}

\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Technical \& Programming:} Advanced LaTeX, Mathematical Modeling, Data Analysis, Numerical Simulation, Python.
    \item \textbf{Languages:} English (Professional Working Proficiency - \textit{C1/C2 certification in progress}), Spanish (Native), Catalan (Native).
    \item \textbf{Core Competencies:} Quantitative Analysis, Complex Problem Solving, Cross-cultural Adaptability, Self-directed Learning.
\end{itemize}

\end{document}